\EVOSUITE at the SBST 2019 Tool Competition

### 2019-03-16 papers/sbst19/paper_sbst19.tex
SBST'19 init commit.

%--------1---------2---------3---------4---------5---------6---------7
%
% Competition paper
% SBST 2013
% Page limit: 4 pages
%

@@

\newcommand{\TOTALPOINTS}{{687}\xspace}

@@

@@

\copyrightyear{2018} 
\acmYear{2018} 
\setcopyright{acmcopyright}
\acmConference[SBST'18]{SBST'18:IEEE/ACM 11th International Workshop on Search-Based Software Testing }{May 28--29, 2018}{Gothenburg, Sweden}
\acmBooktitle{SBST'18: SBST'18:IEEE/ACM 11th International Workshop on Search-Based Software Testing , May 28--29, 2018, Gothenburg, Sweden}
\acmPrice{15.00}
\acmDOI{10.1145/3194718.3194729}
\acmISBN{978-1-4503-5741-8/18/05}

@@

%\title{Unit Testing Tool competition: Results for EvoSuite}
\title{\EVOSUITE at the SBST 2018 Tool Competition}

@@

\author{Jos\'e Miguel Rojas}
\affiliation{%
  \institution{Department of Informatics, University of Leicester}
  \city{Leicester}
  \country{United Kingdom}
}
\email{j.rojas@leicester.ac.uk}

\author{Andrea Arcuri}
\affiliation{%
  \institution{Westerdals Oslo ACT, Norway  and University of
    Luxembourg, Luxembourg}
%  \city{Oslo}
%  \country{Norway}
}
\email{arcand@westerdals.no}

@@

\begin{abstract}
  \EVOSUITE is a search-based tool that automatically generates
  executable unit tests for Java code (JUnit tests).  This paper
  summarises the results and experiences of \EVOSUITE's participation
  at the sixth unit testing competition at SBST 2018, where \EVOSUITE
  achieved the highest overall score (\TOTALPOINTS points) for the
  fifth time in six editions of the competition.
\end{abstract}

@@

%------------------------------------------------------------------------- 
\section{Introduction}
The annual unit test generation competition aims to drive and evaluate
progress on unit test generation tools. In the 6th instance of the
competition at the International Workshop on Search-Based Software
Testing (SBST) 2018, several JUnit test generation tools
%two tools, \EVOSUITE and \JTEXPERT\TODO{confirm},
competed on a set of 59 open-source Java classes, and 
% Two other tools,
%\RANDOOP and \TT, and 
existing open-source test suites were used as
baseline. This paper describes the results obtained by the \EVOSUITE
test generation tool~\cite{FrA11c} in this competition. Details about
the procedure of the competition, the technical framework, and the
benchmark classes can be found in~\cite{sbst18competition}.  In this
competition, \EVOSUITE achieved an overall score of \TOTALPOINTS,
which was the highest among the competing and baseline
tools.

@@

  \hline
  \multicolumn{2}{|l|}{Operation} \\
  \hline
  Interaction &  Through the command line, and plugins for IntelliJ, Maven and Eclipse\\
  User guidance &  Manual verification of assertions for functional faults\\
  Source of information &  http://www.evosuite.org \\
  Maturity&  Mature research prototype, under development\\
  Technology behind the tool & Search-based testing / whole test suite generation\\
\hline
  \multicolumn{2}{|l|}{Obtaining the tool and information} \\
  \hline
License & Lesser GPL V.3\\
Cost & Open source\\
Support & None \\
\hline
\hline
  \multicolumn{2}{|l|}{Does there exist empirical evidence about} \\
  \hline
  Effectiveness and Scalability & See~\cite{GoA_TSE12,fraser2014large} \\
%Completeness & \\
%Effectiveness & \\
%Efficiency & \\
%Defect types & \\
%Scalability & \\
%Comprehensibility & \\
%Learnability & \\
%Subjective satisfaction & \\
%Other & \\
\hline
\end{tabular}\vspace{-1em}
}
\end{table}

@@

The underlying genetic algorithm uses test suites as representation
(chromosomes). Each test suite consists of a variable number of test
cases, each of which is represented as a variable-length sequence of
Java statements (e.g., calls on the class under test). A population of
randomly generated individuals is evolved using suitable search
operators (e.g., selection, crossover and mutation), such that
iteratively better solutions with respect to the optimisation target
are produced. The optimisation target is to maximise code coverage. To
achieve this, the fitness function uses standard heuristics such as
the branch distance; see~\cite{GoA_TSE12} for more details. \EVOSUITE
can be configured to optimise for multiple coverage criteria at the
same time, and the default configuration combines branch coverage with
mutation testing~\cite{emse14_mutation} and other basic
criteria~\cite{rojas2015combining}. Once the search is completed,
\EVOSUITE applies various optimisations to improve the readability of
the generated tests. For example, tests are minimised, and a
minimised set of effective test assertions is selected using mutation
analysis~\cite{10.1109/TSE.2011.93}. For more details on the tool and
its abilities we refer to~\cite{FrA11c,FrA13a}.

The effectiveness of \EVOSUITE has been evaluated on open source as
well as industrial software in terms of code
coverage~\cite{fraser2014large,emse_archive}, fault finding
effectiveness~\cite{shamshiri2015automatically,moein2017}, and effects
on developer
productivity~\cite{TOSEM_userstudy,ISSTA15_Study} and software
maintenance~\cite{ICST2018_Maintenance}.

\EVOSUITE has a longstanding record of success at the unit testing
tool competition, having ranked second in the third edition of the
competition~\cite{evosuiteAtSbst2015} and first in all the other
editions~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013,evosuiteAtSbst2016,evosuiteAtSbst2017}.

@@

The configuration of \EVOSUITE for the 2018 competition is largely
based on its default values, since these have been tuned
extensively~\cite{arcuri2013parameter}. We used the default set of
coverage criteria~\cite{rojas2015combining} (e.g., line coverage,
branch coverage, branch coverage by direct method invocation, weak
mutation testing, output coverage, exception coverage). \EVOSUITE uses
an archive of solutions~\cite{emse_archive} to keep the search focused
on uncovered goals, iteratively discarding covered goals and storing
the tests that covered them. After a certain percentage of the search
budget has passed and with a certain probability, \EVOSUITE starts
using mock objects (relying on Mockito) instead of actual class
instances~\cite{ICST_Mocking17} for dependencies; only branches that
cannot be covered without mocks lead to tests with mock objects. As in
the previous instance of the competition, we continue to use
frequency-based weighted constants for
seeding~\cite{sakti2015instance} and support Java Enterprise Edition
features~\cite{arcuri2016java}. %\TODO{any other noteworthy change?} No.
\EVOSUITE is actively maintained, therefore several bug fixes and
minor improvements have been applied since the last instance of the
competition, in particular in relation to non-determinism and flaky
tests~\cite{arcuri2014automated}, as well as new types of test
assertions (e.g., related to arrays and standard container classes).

@@

\begin{table*}[t]
  \centering
  \caption{\label{table:results}Detailed results of \EVOSUITE on the
    SBST benchmark classes.}
\vspace{-1em}
\resizebox{0.71\textwidth}{!}{  
\input{mainTable.tex}
}	
\end{table*}

@@

Table~\ref{table:results} lists the branch coverage and mutation
analysis results achieved by \EVOSUITE on all benchmark classes in the
contest. Coverage and mutation scores are generally in the expected
ranges, with clear overall increases for higher time budgets. With the
highest time budget of $240s$, the average branch coverage achieved
was \AvgCovD, lower that last year's 64.6\% for the same time budget,
but the average mutation score was \AvgMutD, higher than last year's
49.6\% for the same time budget.

\paragraph{Manually Written Tests}

This year, the contest also included manually written test suites as
baseline (for 49 out of 59 benchmarks). The results indicate that
there is no significant difference in branch coverage between
\EVOSUITE-generated test suites (avg. \AvgCovEvosuite) and manually
written ones (avg. \AvgCovManual), with Vargha-Delaney's
$A_{12}=\EvoManCovA$ and $p=\EvoManCovPV$. In terms of mutation
scores, surprisingly, the results show that automatically generated
assertions are competitive with manually written ones: the average
\EVOSUITE mutation score for these 49 benchmarks is \AvgMutEvosuite
and the average mutation score obtained by developer-written test
suites is \AvgMutManual ($A_{12}=\EvoManMutA$ and
$p=\EvoManMutPV$).

@@

~\EVOSUITE generated \FlakyEvosuite flaky tests per run on average,
much lower than the number of flaky tests produced by the competing
and baseline tools (\FlakyTthree by \TT, \FlakyJtexpert by \JTEXPERT,
and \FlakyRandoop by \RANDOOP). We attribute these relatively positive
results---also consistent with previous years' results---to the way
\EVOSUITE handles execution environments during test generation (e.g.,
controlling the static state of the class under test, mocking
interactions with the file system, system calls like
\texttt{System.in} and \texttt{System.currentTimeMillis},
etc.)~\cite{arcuri2014automated}.  \EVOSUITE provides deterministic
replacement classes for many classes with known non-determinism,
(e.g., those related to date and time), and in particular the FASTJSON
benchmarks made heavy use of these. For example, multiple calendar
systems are necessary (e.g., classes \texttt{HijrahDate},
\texttt{MinguoDate}, \texttt{JapaneseDate},
\texttt{ThaiBuddhistDate}), and \EVOSUITE instantiated its own
replacement versions of these classes 719 times altogether, thus
potentially avoiding many flaky tests. Overall, no flaky tests were
generated for the vast majority of subjects in the competition.

Amongst those benchmarks for which
\EVOSUITE struggled with flakiness, FASTJSON-4 is a notable example:
in the worst case, 90 flaky tests were generated in one single run. An
analysis of the execution logs indicates several possible sources for
this flakiness: a) a non-final static constant that is not properly
reset in between executions; b) a possibly incorrect handling of enum
types; and c) a global property not being reset in between
executions. Considering that there were still remaining flaky tests, further investigation will be needed to confirm these
conjectures and act upon them.

\paragraph{Mocking}

As mentioned in the previous section, \EVOSUITE uses private API
access and functional mocking% in addition to environment
% mocking
~\cite{ICST_Mocking17}. Overall, in all tests generated in this
competition, 1,339 private fields were set and 2,409
private methods were invoked using reflection, and 15,369 Mockito mock
instances were created and configured using another 9,553 statements
(e.g., using the \text{doReturn} method). Considering the 1,804,932 overall test
statements, this means that only 1.4\% of the tests were devoted to
mocking. Amongst the 331 distinct classes for which mocks were
generated at least once there are some classes for which EvoSuite can
instantiate regular objects (e.g., \texttt{List}). This suggests that
EvoSuite sometimes struggles to generate and set up complex objects
correctly, and there is potential for future improvements.

%a total of 2,766 mock
%instances were created, using mocked access. Some of the Java
%classes most frequently used for mocking across benchmarks are
%\texttt{File} (849 instances in total), \texttt{Throwable} (284),
%\texttt{PrintStream} (210) and \texttt{Thread} (114).

% . Further
% investigation would be needed to assess the impact of these mocking
% features on test generation effectiveness for the benchmarks in the
% competition.

@@

~\EVOSUITE failed to produce any test suites for benchmarks DUBBO-2 and
WEBMAGIC-4, and generally struggled with most REDISSON benchmarks
(highlighted in grey in Table~\ref{table:results}). The former two
benchmarks had missing dependencies in the competition
setup~\cite{sbst18competition}, which explains why \EVOSUITE was
incapable of generating any test: When a dependency of the class under
test is missing, then \EVOSUITE intentionally aborts with an error to
inform the user of the configuration error. While this is desirable
behavior during regular usage, arguably in the scope of the
competition \EVOSUITE could try to ignore such errors and try to
generate tests nevertheless, as it might still be possible to cover
code even with some missing dependencies.

For the REDISSON benchmarks, most
executions ended with a timeout; unfortunately, we have not been able
to reproduce this behaviour locally, hence we can only conjecture that
the timeouts (reported during the initialisation phase) are due to the
large number of dependency classes (>7000) that need to be loaded for
these benchmarks to start off the test generation.

@@

This paper reports on the participation of the \EVOSUITE test
generation tool in the 6th SBST Java Unit Testing Tool Contest. With
an overall score of \TOTALPOINTS points, \EVOSUITE achieved the highest score
of all tools in the competition.

@@

%\noindent
\textbf{Acknowledgments:} Many thanks to all the contributors to
\EVOSUITE.  This project has been funded by the EPSRC project
``GREATEST'' (EP/N023978/1), and by the National Research Fund,
Luxembourg (FNR/P10/03).

>>>>

%--------1---------2---------3---------4---------5---------6---------7
%
% Competition paper
% SBST 2019
% Page limit: 4 pages
%

@@

\newcommand{\TOTALPOINTS}{{255.43}\xspace}

@@

\newcommand{\NumCUTS}{{38}\xspace}

@@

\copyrightyear{2019} 
\acmYear{2019} 
\setcopyright{acmcopyright}
\acmConference[SBST'19]{SBST'19: IEEE/ACM 12th International Workshop on Search-Based Software Testing}{May 27, 2019}{Montreal, Canada}
\acmBooktitle{SBST'19: SBST'19: IEEE/ACM 12th International Workshop on Search-Based Software Testing, May 27, 2019, Montreal, Canada}
\acmPrice{15.00}
\acmDOI{}
\acmISBN{}

@@

%\title{Unit Testing Tool competition: Results for EvoSuite}
\title{\EVOSUITE at the SBST 2019 Tool Competition}

\author{Annibale Panichella}
\affiliation{%
  \institution{Delft University of Technology}
  \city{Delft}
  \country{Netherlands}
}
\email{a.panichella@tudelft.nl}

\author{Jos\'e Campos}
\affiliation{%
  \institution{University of Washington}
  \city{Seattle}
  \country{USA}
}
\email{jmcampos@uw.edu}

@@

@@

\begin{abstract}
  \EVOSUITE is a search-based tool that automatically generates
  executable unit tests for Java code (JUnit tests).  This paper
  summarises the results and experiences of \EVOSUITE's participation
  at the seventh unit testing competition at SBST 2019, where \EVOSUITE
  achieved the highest overall score (\TOTALPOINTS points) for the
  sixth time in seven editions of the competition.
\end{abstract}

@@

%------------------------------------------------------------------------- 
\section{Introduction}
The annual unit test generation competition aims to drive and evaluate
progress on unit test generation tools. In the 7th instance of the
competition at the International Workshop on Search-Based Software
Testing (SBST) 2019, several JUnit test generation tools
%two tools, \EVOSUITE and \JTEXPERT\TODO{confirm},
competed on a set of \NumCUTS open-source Java classes. %, and 
% Two other tools,
%\RANDOOP and \TT, and 
%existing open-source test suites were used as
%baseline.
This paper describes the results obtained by the \EVOSUITE
test generation tool~\cite{FrA11c} in this competition. Details about
the procedure of the competition, the technical framework, and the
benchmark classes can be found in~\cite{sbst19competition}.  In this
competition, \EVOSUITE achieved an overall score of \TOTALPOINTS,
which was the highest among the competing and baseline
tools.

@@

  \hline
  \multicolumn{2}{|l|}{Operation} \\
  \hline
  Interaction &  Through the command line, and plugins for IntelliJ, Maven and Eclipse\\
  User guidance &  Manual verification of assertions for functional faults\\
  Source of information &  http://www.evosuite.org \\
  Maturity&  Mature research prototype, under development\\
  Technology behind the tool & Search-based testing / whole test suite generation \TODO{not whole test suite anymore}\\
\hline
  \multicolumn{2}{|l|}{Obtaining the tool and information} \\
  \hline
License & Lesser GPL V.3\\
Cost & Open source\\
Support & None \\
\hline
\hline
  \multicolumn{2}{|l|}{Does there exist empirical evidence about} \\
  \hline
  Effectiveness and Scalability & See~\cite{GoA_TSE12,fraser2014large} \\
%Completeness & \\
%Effectiveness & \\
%Efficiency & \\
%Defect types & \\
%Scalability & \\
%Comprehensibility & \\
%Learnability & \\
%Subjective satisfaction & \\
%Other & \\
\hline
\end{tabular}\vspace{-1em}
}
\end{table}

@@

\TODO{introduce DynaMOSA}
The underlying genetic algorithm uses test suites as representation
(chromosomes). Each test suite consists of a variable number of test
cases, each of which is represented as a variable-length sequence of
Java statements (e.g., calls on the class under test). A population of
randomly generated individuals is evolved using suitable search
operators (e.g., selection, crossover and mutation), such that
iteratively better solutions with respect to the optimisation target
are produced. The optimisation target is to maximise code coverage. To
achieve this, the fitness function uses standard heuristics such as
the branch distance; see~\cite{GoA_TSE12} for more details. \EVOSUITE
can be configured to optimise for multiple coverage criteria at the
same time, and the default configuration combines branch coverage with
mutation testing~\cite{emse14_mutation} and other basic
criteria~\cite{rojas2015combining}. Once the search is completed,
\EVOSUITE applies various optimisations to improve the readability of
the generated tests. For example, tests are minimised, and a
minimised set of effective test assertions is selected using mutation
analysis~\cite{10.1109/TSE.2011.93}. For more details on the tool and
its abilities we refer to~\cite{FrA11c,FrA13a}.

The effectiveness of \EVOSUITE has been evaluated on open source as
well as industrial software in terms of code
coverage~\cite{fraser2014large,emse_archive,ea_evaluation}, fault finding
effectiveness~\cite{shamshiri2015automatically,moein2017}, and effects
on developer
productivity~\cite{TOSEM_userstudy,ISSTA15_Study} and software
maintenance~\cite{ICST2018_Maintenance}.

\EVOSUITE has a longstanding record of success at the unit testing
tool competition, having ranked second in the third edition of the
competition~\cite{evosuiteAtSbst2015} and first in all the other
editions~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013,evosuiteAtSbst2016,evosuiteAtSbst2017,evosuiteAtSbst2018}.

@@

The configuration of \EVOSUITE for the 2019 competition is largely
based on its default values, since these have been tuned
extensively~\cite{arcuri2013parameter}. We used the default set of
coverage criteria~\cite{rojas2015combining} (e.g., line coverage,
branch coverage, branch coverage by direct method invocation, weak
mutation testing, output coverage, exception coverage). \EVOSUITE uses
an archive of solutions~\cite{emse_archive} to keep the search focused
on uncovered goals, iteratively discarding covered goals and storing
the tests that covered them. After a certain percentage of the search
budget has passed and with a certain probability, \EVOSUITE starts
using mock objects (relying on Mockito) instead of actual class
instances~\cite{ICST_Mocking17} for dependencies; only branches that
cannot be covered without mocks lead to tests with mock objects. As in
the previous instance of the competition, we continue to use
frequency-based weighted constants for
seeding~\cite{sakti2015instance} and support Java Enterprise Edition
features~\cite{arcuri2016java}. %\TODO{any other noteworthy change?} No.
\EVOSUITE is actively maintained, therefore several bug fixes and
minor improvements have been applied since the last instance of the
competition, in particular in relation to non-determinism and flaky
tests~\cite{arcuri2014automated}, as well as new types of test
assertions (e.g., related to arrays and standard container classes).

@@

\begin{table*}[t]
  \centering
  \caption{\label{table:results}Detailed results of \EVOSUITE on the
    SBST benchmark classes.}
\vspace{-1em}
\resizebox{\textwidth}{!}{  
\input{mainTable.tex}
}	
\end{table*}

@@

\TODO{}

%Table~\ref{table:results} lists the branch coverage and mutation
%analysis results achieved by \EVOSUITE on all benchmark classes in the
%contest. Coverage and mutation scores are generally in the expected
%ranges, with clear overall increases for higher time budgets. With the
%highest time budget of $240s$, the average branch coverage achieved
%was \AvgCovD, lower that last year's 64.6\% for the same time budget,
%but the average mutation score was \AvgMutD, higher than last year's
%49.6\% for the same time budget.

%\paragraph{Manually Written Tests}

%This year, the contest also included manually written test suites as
%baseline (for 49 out of 59 benchmarks). The results indicate that
%there is no significant difference in branch coverage between
%\EVOSUITE-generated test suites (avg. \AvgCovEvosuite) and manually
%written ones (avg. \AvgCovManual), with Vargha-Delaney's
%$A_{12}=\EvoManCovA$ and $p=\EvoManCovPV$. In terms of mutation
%scores, surprisingly, the results show that automatically generated
%assertions are competitive with manually written ones: the average
%\EVOSUITE mutation score for these 49 benchmarks is \AvgMutEvosuite
%and the average mutation score obtained by developer-written test
%suites is \AvgMutManual ($A_{12}=\EvoManMutA$ and
%$p=\EvoManMutPV$).

@@

\TODO{}

%~\EVOSUITE generated \FlakyEvosuite flaky tests per run on average,
%much lower than the number of flaky tests produced by the competing
%and baseline tools (\FlakyTthree by \TT, \FlakyJtexpert by \JTEXPERT,
%and \FlakyRandoop by \RANDOOP). We attribute these relatively positive
%results---also consistent with previous years' results---to the way
%\EVOSUITE handles execution environments during test generation (e.g.,
%controlling the static state of the class under test, mocking
%interactions with the file system, system calls like
%\texttt{System.in} and \texttt{System.currentTimeMillis},
%etc.)~\cite{arcuri2014automated}.  \EVOSUITE provides deterministic
%replacement classes for many classes with known non-determinism,
%(e.g., those related to date and time), and in particular the FASTJSON
%benchmarks made heavy use of these. For example, multiple calendar
%systems are necessary (e.g., classes \texttt{HijrahDate},
%\texttt{MinguoDate}, \texttt{JapaneseDate},
%\texttt{ThaiBuddhistDate}), and \EVOSUITE instantiated its own
%replacement versions of these classes 719 times altogether, thus
%potentially avoiding many flaky tests. Overall, no flaky tests were
%generated for the vast majority of subjects in the competition.

%Amongst those benchmarks for which
%\EVOSUITE struggled with flakiness, FASTJSON-4 is a notable example:
%in the worst case, 90 flaky tests were generated in one single run. An
%analysis of the execution logs indicates several possible sources for
%this flakiness: a) a non-final static constant that is not properly
%reset in between executions; b) a possibly incorrect handling of enum
%types; and c) a global property not being reset in between
%executions. Considering that there were still remaining flaky tests, further investigation will be needed to confirm these
%conjectures and act upon them.

%\paragraph{Mocking}

%As mentioned in the previous section, \EVOSUITE uses private API
%access and functional mocking% in addition to environment
%% mocking
%~\cite{ICST_Mocking17}. Overall, in all tests generated in this
%competition, 1,339 private fields were set and 2,409
%private methods were invoked using reflection, and 15,369 Mockito mock
%instances were created and configured using another 9,553 statements
%(e.g., using the \text{doReturn} method). Considering the 1,804,932 overall test
%statements, this means that only 1.4\% of the tests were devoted to
%mocking. Amongst the 331 distinct classes for which mocks were
%generated at least once there are some classes for which EvoSuite can
%instantiate regular objects (e.g., \texttt{List}). This suggests that
%EvoSuite sometimes struggles to generate and set up complex objects
%correctly, and there is potential for future improvements.

%%a total of 2,766 mock
%%instances were created, using mocked access. Some of the Java
%%classes most frequently used for mocking across benchmarks are
%%\texttt{File} (849 instances in total), \texttt{Throwable} (284),
%%\texttt{PrintStream} (210) and \texttt{Thread} (114).

%% . Further
%% investigation would be needed to assess the impact of these mocking
%% features on test generation effectiveness for the benchmarks in the
%% competition.

@@

\TODO{why did we get 0\% coverage on most AUTHZFORCE benchmarks? and SPOON-169,
SPOON-25?}

\TODO{why did we get 0\% coverage on DUBBO-2 and WEBMAGIC-4? classpath was
incorrect.}

\TODO{what did we get 0\% coverage on SPOON-253, SPOON-20, SPOON-16, SPOON-155
for larger search budgets?}

\TODO{why did not we get data for FASTJSON-1, FASTJSON-3, FESCAR-41, FESCAR-42,
SPOON-105 for a search budget of 10 seconds?}

%~\EVOSUITE failed to produce any test suites for benchmarks DUBBO-2 and
%WEBMAGIC-4, and generally struggled with most REDISSON benchmarks
%(highlighted in grey in Table~\ref{table:results}). The former two
%benchmarks had missing dependencies in the competition
%setup~\cite{sbst18competition}, which explains why \EVOSUITE was
%incapable of generating any test: When a dependency of the class under
%test is missing, then \EVOSUITE intentionally aborts with an error to
%inform the user of the configuration error. While this is desirable
%behavior during regular usage, arguably in the scope of the
%competition \EVOSUITE could try to ignore such errors and try to
%generate tests nevertheless, as it might still be possible to cover
%code even with some missing dependencies.

%For the REDISSON benchmarks, most
%executions ended with a timeout; unfortunately, we have not been able
%to reproduce this behaviour locally, hence we can only conjecture that
%the timeouts (reported during the initialisation phase) are due to the
%large number of dependency classes (>7000) that need to be loaded for
%these benchmarks to start off the test generation.

@@

This paper reports on the participation of the \EVOSUITE test
generation tool in the 7th SBST Java Unit Testing Tool Contest. With
an overall score of \TOTALPOINTS points, \EVOSUITE achieved the highest score
of all tools in the competition.

@@

%\noindent
\textbf{Acknowledgments:} Many thanks to all the contributors to
\EVOSUITE.  This project has been funded by the EPSRC project
``GREATEST'' (EP/N023978/1), and by the National Research Fund,
Luxembourg (FNR/P10/03). \TODO{update}
